---
title: "Introduction to MDPIexploreR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to MDPIexploreR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MDPIexploreR)
```

# Obtaining list of journals

To retrieve the most current list of MDPI journals, the `MDPIexploreR` package utilizes the `MDPI_journals()` function. This function fetches data from the official MDPI journals page at [https://www.mdpi.com/about/journals](https://www.mdpi.com/about/journals) and generates a table containing the names of the journals along with their corresponding codes.

```{r}
MDPI_journals()|>head(10)
```

These journal codes can then be used across the multiple functions of `MDPIexploreR`. 

# Article level information

`MDPIexploreR` makes easy to obtain a list of all articles published in a journal. For example, to get a list of all articles published in the journal "MDPI Covid" we just need to do:

```{r}
article_find("covid")|>head(5)
```
Extracting editorial information from an article can be done with: 
```{r}
article_info("https://www.mdpi.com/2673-8112/1/1/4")
```

